One page description

### 2016-09-30 publications/Journal/conclusion.tex
Initial section of pdevs.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

\subsection{Conclusions on Performance Evaluation}
We have shown that our contribution is invaluable for high performance simulation: depending on the expected behaviour, modellers can choose the most appropriate synchronization protocol.
But even with the right synchronization protocol, we have seen that two problems remain.

>>>>

\subsection{Conclusions on Performance Evaluation}
We have shown that our contribution is invaluable for high performance simulation: depending on the expected behaviour, modellers can choose the most appropriate synchronization protocol.
PDEVS is compared with the synchronziation protocols either in isolation or complementing each other. We have shown that % continue results
But even with the right synchronization protocol, we have seen that two problems remain.
